\sysfull

### 2018-04-15 paper/systemdescription.tex
enrich the system overview

\textbf{\sys Task Coalescing Manager.} \sys relies on its task coalescing manager to dynamically {\em coalesce} statically\hyp{}defined tasks to avoid inessential overheads associated with completing tasks. By default, tasks run in a sequence and each task commits its task-shared state as it completes.  The time and energy cost of a task's commit is unnecessary if the task and its successor both complete without a power failure. The key insight that \sys leverages is that the first task could have deferred its commit to the second task. {\em coalescing} tasks by deferring the first commit avoids the fixed cost of the first commit (task transitioning overheads). Coalescing also amortizes per-variable commit cost, committing each location accessed by both tasks only after the second task, rather than once per task. \textcolor{red}{\sys's coalescing manager is an \emph{energy-aware manager}. It uses the recent execution history---pure software technique---as a metric to estimate the amount of the available energy and to set the adequate coalesced task size accordingly. This fundamental feature prevents \sys from blind coalesced task adaptation which can result in a repeated power failures problem. For example, If \sys enlarges the coalesced task size by $x$ static tasks on a coalesced task completion and reduces it by the same number of static tasks on a power reboot, then \sys may need to reboot, for instance, 10 times to reduce a coalesced task size from 10 to one, when $x=1$}

Details of coalescing are presented in Section~\ref{sec:task_coalescing}.

\textbf{\sys Task Downscaling Manager.} \sys's downscaling manager is responsible for preserving the forward progress when \sys repeatedly fails on a single static task. The downscaling manager utilizes a timer-based technique and relies on the virtual memory manager to gain a full \emph{flexibility} on where to split a task. These features distinguish \sys task splitting technique from the traditional checkpointing. A checkpointing system that uses voltage threshold to place a checkpoint might cause a program to crash if the checkpoint happened to be placed between a peripheral initialization and its call. If a programmer disables the interrupts around this section of the code, the program may fail indefinitely to progress since the checkpoint may only be deferred. On a repeated failure the \sys task downscaling manager places the \emph{partial commit} after a shorter time than the one before to guarantee forward progress. Details of task downscaling are presented in Section~\ref{sec:task_downsizing}.}

>>>>

\textbf{\sys Task Coalescing Manager.} \sys relies on its task coalescing manager to dynamically {\em coalesce} statically\hyp{}defined tasks to avoid inessential overheads associated with completing tasks. By default, tasks run in a sequence and each task commits its task-shared state as it completes.  The time and energy cost of a task's commit is unnecessary if the task and its successor both complete without a power failure. The key insight that \sys leverages is that the first task could have deferred its commit to the second task. {\em coalescing} tasks by deferring the first commit avoids the fixed cost of the first commit (task transitioning overheads). Coalescing also amortizes per-variable commit cost, committing each location accessed by both tasks only after the second task, rather than once per task. \textcolor{red}{\sys's coalescing manager is an \emph{energy-aware manager}. It uses the recent execution history---pure software technique---as a metric to estimate the amount of the available energy and to set the adequate coalesced task size accordingly. This fundamental feature prevents \sys from blind coalesced task adaptation which may result in a repeated power failure problem. For example, If \sys enlarges the coalesced task size by $x$ static tasks on a coalesced task completion and reduces it by the same number of static tasks on a power reboot, then \sys may need to reboot, for instance, 10 times to reduce a coalesced task size from 10 to one, when $x=1$}. Details of coalescing are presented in Section~\ref{sec:task_coalescing}.

\textbf{\sys Task Downscaling Manager.} \textcolor{red}{\sys's downscaling manager is responsible for preserving the forward progress when \sys repeatedly fails on a single static task. The downscaling manager utilizes a timer-based technique and relies on the virtual memory manager to gain a full \emph{flexibility} on where to split a task. These features distinguish \sys task splitting technique from the traditional checkpointing. A checkpointing system that uses voltage threshold to place a checkpoint might cause a program to crash if the checkpoint happened to be placed between a peripheral initialization and its call. If a programmer disables the interrupts around this section of the code, the program may fail indefinitely to progress since the checkpoint may only be deferred. On a repeated failure the \sys task downscaling manager places the \emph{partial commit} after a shorter time than the one before to guarantee forward progress. Details of task downscaling are presented in Section~\ref{sec:task_downsizing}.}
